A Typed Programmatic Interface to Contracts on the Blockchain

### 2021-06-09 papers/execution-model/APLAS 2021/paper.tex

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 of 2017/10/04
%
\documentclass[runningheads]{llncs}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage{mathpartir}
\usepackage{fixme}
\usepackage{xcolor}
\usepackage{listings}
\lstdefinelanguage{michelson}{
%  basicstyle=\ttfamily,
  morekeywords={parameter,storage,or,unit,mutez,pair,bool,address}, sensitive=false,
  morecomment=[l]{\#},
  morecomment=[s]{/*}{*/},
  morestring=[b]",
}
\lstset{language=Caml}
\input{macros}
%
\usepackage{graphicx}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}

@@

For concreteness, Listing~\ref{lst:auction-contract-header} shows the
header of an auction contract in Michelson \cite{michelson}. The
\lstinline/parameter/ clause specifies the contract's parameter
type. It is a sum type (indicated by \lstinline/or/) and each
alternative constitutes an entrypoint, named \lstinline/%close/ and
\lstinline/%bid/. The caller selects the entrypoint by injecting the argument into the
\lstinline/left/ or \lstinline/right/ summand. Both entrypoints take a \lstinline{unit}
parameter. The \lstinline/%bid/ entrypoint considers the transferred
tokens as the bid.
The \lstinline/storage/ clause declares the state of the contract,
which is a nested pair type indicating whether bidding is allowed
(\lstinline{bool}), the address of the contract owner (to prohibit
unauthorized calls to \lstinline/%close/), and the bidder's
address. The highest bid corresponds to the token balance of the contract.
\begin{lstlisting}[language=michelson,numbers=none,float,caption={Header of the auction contract},label={lst:auction-contract-header},captionpos=b,emph={close,bid},emphstyle=\underbar]
parameter (or (unit %close)
              (unit %bid)); # bid in transfer
storage (pair bool          # bidding allowed
         (pair address      #  contract owner
          address           # highest bidder's address
        ));
\end{lstlisting}

@@

First the code that creates an auction contract and closes it after 48 hours. 
\begin{lstlisting}[language=Caml,numbers=none,basicstyle=\small]
let _ = Cl.set_authority (my_address)
let initial_store = (true, (my_address, my_address))
let contract = Cl.originate(auction_script, 1, initial_store)
Time.sleep(48 * 3600);               (* 48h in seconds *)
Cl.call_contract(contract, left ()); (* entrypoint %close *)
\end{lstlisting}
We assume that \lstinline/Cl/ is the module containing the contract
library, \lstinline{set_authority} sets the sender address for
upcoming operations,  \lstinline/originate/ deploys its argument contract along
with the provided funds of one token and the \lstinline/initial_store/, 
\lstinline{auction_script} is the contract from Listing~\ref{lst:auction-contract-header}, and 
\lstinline{call_contract} invokes a contract with a parameter. The
\lstinline{initial_store} sets the bidding flag, and both owner and
highest bidder to the sender account.

To implement the bidding strategy, we first check the state of the
contract to find the current highest bid. As long as bidding is
allowed and the current bid is below our \lstinline/limit/, we update
our bid by a given amount \lstinline/step/, and then keep watching the state of the contract by
polling it every five minutes. 
\begin{lstlisting}[numbers=none,basicstyle=\small]
let rec poll (limit, step, ((bidding, _), (high_bid, _))) =
  if bidding and high_bid < limit then
    Cl.call_contract (contract, 
      right (min (high_bid + step, limit))); (* entrypoint %bid *)
    Time.sleep(5 * 60);
    let state = Cl.get_state (contract);
    poll (limit, step, state)
in
poll (limit, step, Cl.get_state (contract))
\end{lstlisting}
The \lstinline{get_state} function obtains the storage of a contract from
the blockchain.

@@

\subsection{A Subsection Sample}
Please note that the first paragraph of a section or subsection is
not indented. The first paragraph that follows a table, figure,
equation etc. does not need an indent, either.

Subsequent paragraphs, however, are indented.

\subsubsection{Sample Heading (Third Level)} Only two levels of
headings should be numbered. Lower level headings remain unnumbered;
they are formatted as run-in headings.

\paragraph{Sample Heading (Fourth Level)}
The contribution should contain no more than four levels of
headings. Table~\ref{tab1} gives a summary of all heading levels.

\begin{table}
\caption{Table captions should be placed above the
tables.}\label{tab1}
\begin{tabular}{|l|l|l|}
\hline
Heading level &  Example & Font size and style\\
\hline
Title (centered) &  {\Large\bfseries Lecture Notes} & 14 point, bold\\
1st-level heading &  {\large\bfseries 1 Introduction} & 12 point, bold\\
2nd-level heading & {\bfseries 2.1 Printing Area} & 10 point, bold\\
3rd-level heading & {\bfseries Run-in Heading in Bold.} Text follows & 10 point, bold\\
4th-level heading & {\itshape Lowest Level Heading.} Text follows & 10 point, italic\\
\hline
\end{tabular}
\end{table}

\noindent Displayed equations are centered and set on a separate
line.
\begin{equation}
x + y = z
\end{equation}
Please try to avoid rasterized images for line-art diagrams and
schemas. Whenever possible, use vector graphics instead (see
Fig.~\ref{fig1}).

\begin{figure}
\includegraphics[width=\textwidth]{fig1.eps}
\caption{A figure caption is always placed below the illustration.
Please note that short captions are centered, while long ones are
justified by the macro package automatically.} \label{fig1}
\end{figure}

\begin{theorem}
This is a sample theorem. The run-in heading is set in bold, while
the following text appears in italics. Definitions, lemmas,
propositions, and corollaries are styled the same way.
\end{theorem}
%
% the environments 'definition', 'lemma', 'proposition', 'corollary',
% 'remark', and 'example' are defined in the LLNCS documentclass as well.
%
\begin{proof}
Proofs, examples, and remarks have the initial word in italics,
while the following text appears in normal font.
\end{proof}
For citations of references, we prefer the use of square brackets
and consecutive numbers. Citations using labels or the author/year
convention are also acceptable. The following bibliography provides
a sample reference list with entries for journal
articles~\cite{ref_article1}, an LNCS chapter~\cite{ref_lncs1}, a
book~\cite{ref_book1}, proceedings without editors~\cite{ref_proc1},
and a homepage~\cite{ref_url1}. Multiple citations are grouped
\cite{ref_article1,ref_lncs1,ref_book1},
\cite{ref_article1,ref_book1,ref_proc1,ref_url1}.
%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
% \bibliographystyle{splncs04}
% \bibliography{mybibliography}
%
\begin{thebibliography}{8}
\bibitem{ref_article1}
Author, F.: Article title. Journal \textbf{2}(5), 99--110 (2016)

\bibitem{ref_lncs1}
Author, F., Author, S.: Title of a proceedings paper. In: Editor,
F., Editor, S. (eds.) CONFERENCE 2016, LNCS, vol. 9999, pp. 1--13.
Springer, Heidelberg (2016). \doi{10.10007/1234567890}

\bibitem{ref_book1}
Author, F., Author, S., Author, T.: Book title. 2nd edn. Publisher,
Location (1999)

\bibitem{ref_proc1}
Author, A.-B.: Contribution title. In: 9th International Proceedings
on Proceedings, pp. 1--2. Publisher, Location (2010)

\bibitem{ref_url1}
LNCS Homepage, \url{http://www.springer.com/lncs}. Last accessed 4
Oct 2017
\end{thebibliography}
\end{document}

>>>>

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 of 2017/10/04
%
\documentclass[runningheads]{llncs}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage{mathpartir}
\usepackage{fixme}
\usepackage{xcolor}
\usepackage{listings}
\lstdefinelanguage{michelson}{
%  basicstyle=\ttfamily,
  morekeywords={parameter,storage,or,unit,mutez,pair,bool,address}, sensitive=false,
  morecomment=[l]{\#},
  morecomment=[s]{/*}{*/},
  morestring=[b]",
}
\lstset{language=Caml}
\input{macros}

@@

For concreteness, Listing~\ref{lst:auction-contract-header} shows the
header of an auction contract in Michelson \cite{michelson}. The
\lstinline/parameter/ clause specifies the contract's parameter
type. It is a sum type (indicated by \lstinline/or/) and each
alternative constitutes an entrypoint, named \lstinline/%close/ and
\lstinline/%bid/. The caller selects the entrypoint by injecting the argument into the
\lstinline/left/ or \lstinline/right/ summand. Both entrypoints take a \lstinline/unit/
parameter. The \lstinline/%bid/ entrypoint considers the transferred
tokens as the bid.
The \lstinline/storage/ clause declares the state of the contract,
which is a nested pair type indicating whether bidding is allowed
(\lstinline/bool/), the address of the contract owner (to prohibit
unauthorized calls to \lstinline/%close/), and the bidder's
address. The highest bid corresponds to the token balance of the contract.
\begin{lstlisting}[language=michelson,numbers=none,float,caption={Header of the auction contract},label={lst:auction-contract-header},captionpos=b,emph={close,bid},emphstyle=\underbar]
parameter (or (unit %close)
              (unit %bid)); # bid in transfer
storage (pair bool          # bidding allowed
         (pair address      #  contract owner
          address           # highest bidder's address
        ));
\end{lstlisting}

@@

First the code that creates an auction contract and closes it after 48 hours.

\begin{lstlisting}[language=Caml,numbers=none,basicstyle=\small]
let _ = Cl.set_authority (my_address)
let initial_store = (true, (my_address, my_address))
let contract = Cl.originate(auction_script, 1, initial_store)
Time.sleep(48 * 3600);               (* 48h in seconds *)
Cl.call_contract(contract, left ()); (* entrypoint %close *)
\end{lstlisting}

We assume that \lstinline!Cl! is the module containing the contract
library, \lstinline/set_authority/ sets the sender address for
upcoming operations,  \lstinline/originate/ deploys its argument contract along
with the provided funds of one token and the \lstinline/initial_store/
\lstinline/auction_script/ is the contract from Listing~\ref{lst:auction-contract-header}, and 
\lstinline/call_contract/ invokes a contract with a parameter. The
\lstinline/initial_store/ sets the bidding flag, and both owner and
highest bidder to the sender account.

To implement the bidding strategy, we first check the state of the
contract to find the current highest bid. As long as bidding is
allowed and the current bid is below our \lstinline/limit/, we update
our bid by a given amount \lstinline/step/, and then keep watching the state of the contract by
polling it every five minutes.

\begin{lstlisting}[numbers=none,basicstyle=\small]
let rec poll (limit, step, ((bidding, _), (high_bid, _))) =
  if bidding and high_bid < limit then
    Cl.call_contract (contract, 
      right (min (high_bid + step, limit))); (* entrypoint %bid *)
    Time.sleep(5 * 60);
    let state = Cl.get_state (contract);
    poll (limit, step, state)
in
poll (limit, step, Cl.get_state (contract))
\end{lstlisting}

The \lstinline/get_state/ function obtains the storage of a contract from
the blockchain.

@@
